systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-23 paper/branches/useR2006/systemfit.tex
branches/useR2006: added abstract for useR 2006
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@626 591db2bd-e0a0-4d22-8c19-2192dbb7da31

%       $Id$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% For all of the methods developed in the package, the disturbances of
% the individual equations are assumed to be independent and identically
% distributed (iid).  
% In the future, we would like to add the ability to fit equations were
% the disturbances are serially correlated (wikins 1969).

The \pkg{systemfit} package provides the capability to estimate
linear equation systems in \proglang{R}
\citep{r-project}.
Although linear equation systems can be estimated
with several other statistical and econometric software packages
(e.g.\ \proglang{SAS}, \proglang{EViews}, \proglang{TSP}),
\pkg{systemfit} has several advantages.
First, all estimation procedures are publicly available in the source code.
Second, the estimation algorithms can be easily modified to meet specific
requirements.
Third, the (advanced) user can control estimation details generally
not available in other software packages by overriding reasonable defaults.

This paper is organized as follows:
In the following Section~\ref{sec:statistics} we
introduce the statistical background of estimating equation systems.
The implementation of the statistical procedures in \proglang{R}
is shortly explained in Section~\ref{sec:code}.
Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit} and especially how the features presented in the previous
section can be used.
In Section~\ref{sec:reliability} the reliability of the results from
\pkg{systemfit} are tested.
Finally, a summary and outlook are presented in
Section~\ref{sec:Summmary}.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "systemfit"
%%% End:

>>>>

\documentclass[12pt]{scrartcl}
\input{systemfit_commands}

\begin{document}

\begin{center}

\title{
systemfit: A Package to Estimate\\
Simultaneous Equation Systems in \proglang{R}
}

\vspace{6mm}

\author{
Arne Henningsen and Jeff D.\ Hamann
}

\end{center}

@@

The \pkg{systemfit} package provides the capability to estimate
linear equation systems in \proglang{R}
\citep{r-project}.
Although linear equation systems can be estimated
with several other statistical and econometric software packages,
\pkg{systemfit} has several advantages.
First, all estimation procedures are publicly available in the source code.
Second, the estimation algorithms can be easily modified to meet specific
requirements.
Third, the (advanced) user can control estimation details generally
not available in other software packages by overriding reasonable defaults.

The \pkg{systemfit} package has been tested on a variety of datasets and
has produced satisfactory for a few years.
On the useR! conference,
we would like to present some of the basic features of the
\pkg{systemfit} package,
some of the many details that can be controlled by the user,
and the statistical tests for parameter restrictions and
consistency of 3SLS estimation that are included in the package.
While the \pkg{systemfit} package performs the basic fitting methods,
more sophisticated methods are still missing.
We hope to implement missing functionalities
in the near future
--- maybe with the help of other useRs.

\bibliographystyle{jss}
\bibliography{systemfit} % a subset of my big bibtex file
%\bibliography{/home/suapm095/Documents/Literatur/arne}

\end{document}
